\documentclass{article}
\usepackage{xeCJK}
\setCJKmainfont{IPAexMincho} % or another Japanese font like Noto Sans CJK
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{soul}   % For highlighting
\usepackage{pgfkeys}
\usepackage{tcolorbox}
\usepackage{pxfonts}
\usepackage{calc}
\usepackage{mdframed}
\pagestyle{empty}
\usepackage{ulem}
\usepackage{fontawesome}

\definecolor{highlightblue}{rgb}{0.91,0.95,1} % Light blue
\definecolor{lightgray}{RGB}{204,204,204}

% Define custom aquamarine color using RGB values
\definecolor{midnightblue}{rgb}{0.0, 0.2, 0.4}
\definecolor{customcolor}{HTML}{E8E8E8}


\hypersetup{
    colorlinks=true,
    linkcolor=midnightblue,
    urlcolor=midnightblue,
}

\usepackage{fontspec}
\setmainfont{Georgia}
\begin{document}

\begin{center}
    \textbf{\LARGE Anton Melnychuk} \\[0.5em]
    +1 (475) 287 8907 \textbullet{} New Haven, CT (F1 visa; CPT Work Authorization) \textbullet{} Ukrainian, Volyn \\
    \href{mailto:anton.melnychuk@yale.edu}{anton.melnychuk@yale.edu} \textbullet{} \href{https://www.linkedin.com/in/antonmelnychuk/}{linkedin.com/in/antonmelnychuk} \textbullet{} \href{https://github.com/anton-mel}{github.com/anton-mel}
\end{center}

% , USA (F1 Student Visa), 1-475-287-8907 \textbar\ \faicon{github}  \url{ https://github.com/anton-mel} \textbar\ anton.melnychuk@yale.edu \\
%  \setstretch{1.2}Undergraduate student | Ukrainian (Native) | Polish (Limited) | English | Japanese (Advanced) \vspace{-2ex}

\vspace{-4ex}
\section*{\vspace{0ex}\textcolor{gray}{\rule[0ex]{0em}{0ex}}\hspace{0em}\normalsize\textnormal{\textcolor{darkgray}{EDUCATION}}\hspace{0.7em}\textcolor{customcolor}{\rule[0.5ex]{\dimexpr\linewidth-6.4em}{0.5pt}}\vspace{-2ex}}
\textbf{Yale University}, BSMS. Computer Science; Focus: EE \& System Engineering
\hfill \textit{May 2026 (Junior)}

\begin{itemize}[topsep=1pt]
\setlength\itemsep{-0.4em}
    \item\setstretch{1.2} \textbf{Relevant Coursework} († - Graduate Level): Principles of Computer System Design$^{\dag}$, Building Distributed Systems$^{\dag}$, System Programming and Computer Organization, Proof-Based Algorithms.
    \item\setstretch{1.2} \textbf{Incoming Coursework:} Computer Architecture$^{\dag}$, Building Network Systems$^{\dag}$, Circuits and Systems Design.
\end{itemize}

\noindent\vspace{-2ex}\textbf{Osaka Gakuin University}, Study Abroad Japan, Intermediate-Advanced Japanese.
\hfill \textit{Jun 2023 - Aug 2023}


\vspace{-1.5ex}
\section*{\vspace{0ex}\textcolor{gray}{\rule[0ex]{0em}{0ex}}\hspace{0em}\normalsize\textnormal{\textcolor{gray}{}}\hspace{8em}\textcolor{customcolor}{\rule[0.5ex]{\dimexpr\linewidth-16em}{0.5pt}}\vspace{-2ex}}

\vspace{0.4em}
\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r @{}}
    \textit{Hard skills:} & \textbf{Rust/C/C++;} Shell; Python, Go, Verilog, x86-asm, Express/ReactNative/React, MongoDB, git\vspace{0.2em} \\
    \textit{Technologies:} & K8s, Docker; Linux; AWS/GCP, CI/CD, PyTorch \& CUDA; OpenCV; RPC/HTTP, ASPICE, Omniverse
    \vspace{0.2em} \\
    \textit{Languages:} & English (Fluent); Russian (Bilingual); Ukrainian (Native); Japanese (Advanced); Polish (Limited)\vspace{0.2em} 
\end{tabular*}

\vspace{-2ex}
\section*{\vspace{0ex}\textcolor{gray}{\rule[0ex]{0em}{0ex}}\hspace{0em}\normalsize\textnormal{\textcolor{darkgray}{WORK EXPERIENCE}}\hspace{0.7em}\textcolor{customcolor}{\rule[0.5ex]{\dimexpr\linewidth-9.7em}{0.5pt}}\vspace{-2ex}}

\noindent{\textbf{\href{https://www.ironflight.ai/}{\textbf{Embedded Developer}}}
\hfill \textit{Sep 2024 - Present}\\
\noindent{\textit{Iron Flight}}
\hfill \textit{San Francisco, USA}
\begin{itemize}[topsep=1pt]
\setlength\itemsep{-0.3em}
  \item\setstretch{1.2} Volunteer to built AI-driven autonomous control systems for drones to protect freedom.
  \item\setstretch{1.2} Partitioned an object tracking DNN using Rust for drone-server distributed inference over UDP, optimizing performance by minimizing kernel-user boundary crossings and saving the company over \$100,000 on hardware yearly.
  \item\setstretch{1.2} Developed protocols and modified STM32 flight controllers, boosting drone responsiveness in critical EW zones by 7\%.
\end{itemize} \vspace{0.5ex} 

\noindent{\textbf{\href{https://www.yecl.org/}{\textbf{Operating Systems Research}}}
\hfill \textit{Jan 2024 - Present}\\
\noindent{\textit{Efficient Computing Lab}}
\begin{itemize}[topsep=1pt]
\setlength\itemsep{-0.3em}
  \item\setstretch{1.2} Build and volunteerely redesigned in memory-safe Rust \href{https://www.github.com/anton-mel/WeensyOS}{WeensyOS} (detailed in projects), a tiny but real operating system used in 6+ US universities' core systems course to study kernel address space split and allocation techniques.
  
  \item\setstretch{1.2} Improved modularity in \href{https://github.com/theseus-os/Theseus}{TheseusOS} by shifting responsibilities to the Rust compiler by foregoing hardware privilege levels (e.g., x86's Ring 0-3), reaching 79\% fault recovery over 800k+ injected faults with overheads at most 18\%.
  \item\setstretch{1.2} Modified \href{https://github.com/anton-mel/linux}{Linux kernel} (Ubuntu 22.04) to cross-compile Rust loadable kernel modules, used for graduate-level course.

  \item\setstretch{1.2} Published an OS-verification \href{https://crates.io/crates/proc_assertions}{cargo crate} with 200+ daily downloads.
  
\end{itemize} \vspace{0.5ex}

\noindent{\textbf{\href{https://vision.cs.yale.edu/team/}{\textbf{Computer Vision Research}}}
\hfill \textit{Sep 2023 - Sep 2024 [13 month]}\\
\noindent{\textit{Vision Lab}}
\begin{itemize}[topsep=1pt]
\setlength\itemsep{-0.3em}
  \item\setstretch{1.2} Developed \textit{generative physics AI} model for predicting short-term camera-occluded zone character walking trajectories.
  \item\setstretch{1.2} Built Isaac Sim OpenAI synthetic data generative pipeline gathering 80k+ labels for training.
  \item\setstretch{1.2} Led illicit pill classification project partnered with Swedish National Forensics labs.
  
\end{itemize} \vspace{0.7ex}

\noindent{\textbf{\href{https://yaleaerospace.org/about}{\textbf{Systems Developer}}}
\hfill\textit{Sep 2023 - May 2024 [9 month]}\\
\noindent{\textit{Yale Undergraduate Aerospace Association}}
\begin{itemize}[topsep=1pt]
\setlength\itemsep{-0.3em}
  \item\setstretch{1.2} Assisted in the development of core avionics system partnered with NASA. 
  \item\setstretch{1.2} Tested RTOS signals and logs; implemented satellite power distribution algorithm, reducing consumption by 45\%.
\end{itemize}


\vspace{-2ex}
\section*{\vspace{0ex}\textcolor{gray}{\rule[0ex]{0em}{0ex}}\hspace{0em}\normalsize\textnormal{\textcolor{darkgray}{PROJECTS}}\hspace{0.7em}\textcolor{customcolor}{\rule[0.5ex]{\dimexpr\linewidth-5.4em}{0.5pt}}\vspace{-2ex}}

\noindent{\textbf{Pipelined RISC-V Processor Design}}, Custom CPU \setstretch{1.2} \hfill \textit{Sep 2024 - Present (Ongoing)} 
\begin{itemize}[topsep=1pt]
\setlength\itemsep{-0.2em}
    \item\setstretch{1.2} Designed and implemented a 5-stage pipelined RISC-V processor in Verilog, supporting instructions like lw, addi, beq, and slt. Optimized the control path and memory modules, aiming to reduce instruction latency.
\end{itemize}

\noindent{\href{https://www.github.com/anton-mel/WeensyOS}{\textbf{WeensyOS}}, Custom Operating System \setstretch{1.2} \hfill \textit{May 2024 - July 2024 [3 month]} 
\begin{itemize}[topsep=1pt]
\setlength\itemsep{-0.2em}
    \item\setstretch{1.2} Transitioned a commonly used to teach OS to Rust, 95\%+ reducing unsafe code (implements 15 unsafe blocks).
    \item\setstretch{1.2} Setup statically linked bootloader crate and developed custom GDT/IHM for Intel 8259 PIC, heap memory allocation, polling, and multitasking mechanisms. Implemented processes and a program loader to test Virtual Memory Map.
\end{itemize}








% \noindent{\textbf{Memory Sanitizer}, C Library \setstretch{1.2}
% \hfill \textit{Jan 2024}
% \begin{itemize}[topsep=1pt]
% \setlength\itemsep{0.29em}
%   \item\setstretch{1.2} Designed and build custom debugging memory allocator akin to simplified \texttt{Valgrind} in C to track memory usage, heavy allocation regions, and catch common memory errors (e.g. usage after free, double free, memory leak).
% \end{itemize}

% \noindent\href{https://yalecomputersociety.org/}{\textbf{Yale Clubs (Co-Founder)}}, Yale Computer Society \setstretch{1.2}
% \hfill \textit{Sep 2023 - Jan 2024 [5 month]}
% \begin{itemize}[topsep=1pt]
% \setlength\itemsep{-0.3em}
%   \item\setstretch{1.2} Led a team of 9 students to develop a CRM-based web and iOS cross-platform app for club management at Yale.
%   \item\setstretch{1.2} Increased distributed service robustness and implemented a fallback caching system based on user preferences.
%   \item\setstretch{1.2} Deployed, scaled, and load balanced on GCP using Kubernetes, supporting 80+ clubs and over 2,000 daily users.
% \end{itemize}




% \noindent{\textbf{Building Distributed Systems}}, CPSC 426 Projects [Graduate Level] \setstretch{1.2}
% \hfill \textit{Sep 2024 - Present}
% \begin{itemize}[topsep=1pt]
% \setlength\itemsep{-0.2em}
%   \item\setstretch{1.2} Developed load balancing strategies using consistent hashing and Maglev, improving system scalability by 30\%.
%   \item\setstretch{1.2} Implemented RAFT consensus algorithm in Go, enhancing fault tolerance for distributed systems by 20\%.
%   \item\setstretch{1.2} Managed containerized applications with Kubernetes, building cloud-based distributed ML and networking systems.
% \end{itemize}







\vspace{-3.5ex}
\section*{\vspace{0ex}\textcolor{gray}{\rule[0ex]{0em}{0ex}}\hspace{0em}\normalsize\textnormal{\textcolor{gray}{}}\hspace{8em}\textcolor{customcolor}{\rule[0.5ex]{\dimexpr\linewidth-16em}{0.5pt}}\vspace{-2ex}}



% \section*{\vspace{0ex}\textcolor{gray}{\rule[0ex]{0em}{0ex}}\hspace{0em}\normalsize\textnormal{\textcolor{gray}{CERTIFICATES}}\hspace{0.7em}\textcolor{customcolor}{\rule[0.5ex]{\dimexpr\linewidth-7em}{0.5pt}}\vspace{-2ex}}

% \begin{center}
%   \begin{minipage}[t]{0.47\textwidth}
%     \textbf{Python for Computer Vision} offered by Udemy.
%   \end{minipage}
%   \hfill
%   \begin{minipage}[t]{0.47\textwidth}
%     \textbf{Computer Vision and Image Processing}; IBM, Coursera.
%   \end{minipage}
% \end{center}\vspace{-4ex}



\end{document}
